---
title: "Eating Out"
author: "America Olivo"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5
date: "`r Sys.Date()`"    
    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## There were two years in which the General Social Survey asked about the frequency of eating out.
### Find those years and for the first year the question was asked download that years data in a stata format - its name will be "GSSxxxx.dta" where the xxxx is replaced by the year.  For example if the year was 1983 its name would be GSS1983.dta. Your assignment is to download the GSS yearly dataset for the first year the question was asked and then  write up the answer to the question by editing the  code block in line 31 to eval=TRUE and finish the job. 

$H_0$ There is no difference among the various races with frequency of eating out  
$H_A$ There is a statistical difference between at least two races with the frequency of eating out  


```{r include=FALSE,echo=FALSE}
source(file="fisherXY.R")
require(tidyverse)
require(tigerstats)
require(knitr)
require(foreign)
```
```{r, eval=TRUE}
GSS <-read.dta(file="GSS1996.dta")
GSS <- droplevels(GSS)
mydata <- select(GSS ,race, age, eatout)
mydata <- na.omit(mydata)
```

# Methods 
We will be using a graphical, numerical, and inferential results to figure out if there is a difference among the various races and the way of eating out. Lastly were trying i find if there id a statistical difference between the least , two races with the variable of eating out.


# Graphical

```{r}
barchartGC(~race + eatout, data=mydata)
barchartGC(~race + eatout, data=mydata, type ="percent")
```



This bar chart shows that white people are 85% eating out less than the 20% that dont eat out. 70% of black people eat out and 30% do not. Other races percentage of eating out is about 75% and those who dont are the other 20%. White people eat out the most and black people eat out less between all the groups. The other races are in between the whites and blacks in comparsion of eating out.


#Numerical 

```{r}
table1 <- xtabs(~race +eatout, data=mydata)
rowPerc(table1)
colPerc(table1)
```

The table above shows about 83% of white people eat out and 17% of them who don't. About 69% of black people eat out while there's 31% of those who do not eat out. Lastly other races have about 78% of them who do eat out and there are 22% that dont.
1.White people are most likely to go out to eat
2.Other races are in the middle 
3.Black people are more unlikely to go out to eat


## Inferential


```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```


```{r}
fisherXY(mydata$race, mydata$eatout, printAll = TRUE)
```

As shown above, the fisherXY test shows that there is a statistical difference two groups. White people and black people because of the p-value being 0.0003864 which is way too low. Then the p-value for black people and other races is 0.2815 which is higher/better than our first p-value. This means that there's no statistical difference between the groups. The p-value between white people and other races is the highest at 0.3543. This means that there is no statistical difference. 

## conclusion

The statistical difference is between white people and black people which is proved by the fisherXY test. The relationship also has the lowest p-value compared to the whites and other races which as the highest. 









